---
title: "plotly problem"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: flatly
---


We're going to look at NYC Restaurants data

```{r}
library("p8105.datasets")
library("dplyr")
library("tidyverse")
library("plotly")
library("tidyverse")
library("httr")
library("jsonlite")
```


Data import - NYC Restaurant Data
```{r}

get_all_inspections = function(url) {
  
  all_inspections = vector("list", length = 0)
  
  loop_index = 1
  chunk_size = 50000
  DO_NEXT = TRUE
  
  while (DO_NEXT) {
    message("Getting data, page ", loop_index)
    
    all_inspections[[loop_index]] = 
      GET(url,
          query = list(`$order` = "zipcode",
                       `$limit` = chunk_size,
                       `$offset` = as.integer((loop_index - 1) * chunk_size)
                       )
          ) %>%
      content("text") %>%
      fromJSON() %>%
      as_tibble()
    
    DO_NEXT = dim(all_inspections[[loop_index]])[1] == chunk_size
    loop_index = loop_index + 1
  }
  
  all_inspections
  
}

url = "https://data.cityofnewyork.us/resource/43nn-pn8j.json"

nyc_inspections = 
  get_all_inspections(url) %>%
  bind_rows() 
```

Data Manipulation
```{r}
nyc_subset = 
nyc_inspections %>% 
  filter(grade %in% c("A", "B", "C"), boro == "Manhattan", cuisine_description == "Korean")

view(nyc_subset)
```


# Plotly plots

## scatterplot
This plot describes the grades of each restaurant as compared to the latitude and longitude; there is (as expected) a denser cluster of restaurants in Koreatown. 
```{r}
nyc_subset %>% 
plot_ly(
  x = ~latitude, y = ~longitude, color = ~grade, text = ~dba, alpha = .5,
          type = "scatter", mode = "markers")
```

## boxplot
This plot describes the critical flags as compared to census tracts (areas in which the data were collected). 
```{r}
nyc_subset %>% 
 plot_ly(y = ~census_tract, x = ~critical_flag, color = ~critical_flag,
          type = "box", colors = "viridis")
```


## bar plot
This bar plot describes the number of each restaurant in Manhattan. Based on this figure, Mokja is the most popular Korean chain in Manhattan.
```{r}
nyc_subset %>% 
 count(dba) %>% 
  mutate(restaurant = fct_reorder(dba, n)) %>% 
  plot_ly(x = ~restaurant, y = ~n, colors = "viridis", type = "bar")
```


